### 2025-06-20 evaluating-prediction-accuracy.qmd
20250619 - unamalgating multi-item scales
20250619 - ROC curve

```{r}
#| label: fig-rocCurveExample
#| fig-cap: "Example Receiver Operating Characteristic (ROC) Curve."
#| fig-alt: "Example Receiver Operating Characteristic (ROC) Curve."
#| fig-width: 8
#| fig-height: 6

@@

>>>>

```{r}
#| label: fig-rocCurveExample
#| fig-cap: "Example Receiver Operating Characteristic (ROC) Curve."
#| fig-alt: "Example Receiver Operating Characteristic (ROC) Curve."
#| fig-width: 8
#| fig-height: 8

@@

- Instead of aggregating scores from multiple variables, another option is to "unamalgamate" the predictors, that is, to use each variable as a separate predictor, to maximize predictive power [@TrafimowInPress].
